### 2019-01-18 Sections/economics_of_the_quantum_internet.tex
tiny
Drew quote

@@

This is easily intuitively seen as follows. Let the computational scaling function be an arbitrary exponential,
\begin{align}
f_\mathrm{sc}(n) = O(\mathrm{exp}(n)).	
\end{align}
Then it immediately follows that the scaling function obeys the identity,
\begin{align}
	f_\mathrm{sc}\left(\sum_i n_i \right) = \prod_i f_\mathrm{sc}(n_i),
\end{align}
yielding the multiplicative behaviour.

>>>>

\famousquote{Economics is probably the weirdest academic discipline I've come across. I find myself constantly in a superposition of fascination and annoyance with how the field currently stands. How can smart people have come up with a collection of ideas that are simultaneously brilliant and ridiculous, insightful and delusional, pragmatic and useless?}{Andrew Ringsmuth}

@@

This is easily intuitively seen as follows. Let the computational scaling function be an arbitrary exponential,\index{Multiplicativity in computational power}
\begin{align}
f_\mathrm{sc}(n) = O(\mathrm{exp}(n)).	
\end{align}
Then it immediately follows that the scaling function obeys the identity,
\begin{align}
	f_\mathrm{sc}\left(\sum_i n_i \right) = \prod_i f_\mathrm{sc}(n_i),
\end{align}
yielding the multiplicative behaviour.
